---
title: "Loblolly pine tree data activity"
format: 
  html: 
    embed-resources: true
editor: visual
---

```{r}
#| label: setup
#| echo: false
#| messages: false
#| warning: false

library(tidyverse)
library(esquisse)
library(lorem)
options(scipen = 999, digits = 3)
```


#Description
The Loblolly data frame has 84 rows and 3 columns of records of the growth of Loblolly pine trees.

#Format
height
a numeric vector of tree heights (ft).

age
a numeric vector of tree ages (yr).

Seed
an ordered factor indicating the seed source for the tree. The ordering is according to increasing maximum height.

```{r}
#| label: show the data
head(Loblolly)
```

<p style="page-break-after:always"> </p>

```{r}
#| label: main data chunk
#| echo: true

model <- lm(height ~ age, data = Loblolly)
cat("Tree height =",coef(model)[1],"+",coef(model)[2],"*Age")
summary(model)

ggplot(Loblolly,aes(x = age, y = height, color = Seed, group = Seed)) +
  geom_point(size = 2) +
  geom_smooth(method = "lm", formula = y ~ x,se = FALSE) +
  labs(title = "Growth of Loblolly pine trees", x = "Ages(yrs)", y = "Height(ft)") +
  theme_classic()

```
#Interpret: 
From the graph and summary, we can tell tree's height has a strong linear relationship with tree's age. 

#Repo URL:
https://github.com/MA615-2025Fall-Tingji/Class-8-Sep19
